\documentclass[12pt]{article}

% Load necessary packages
\usepackage{geometry}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{hyperref}

% Set page margins
\geometry{margin=1in}

% Set line spacing
\doublespacing

% Title and author information
\title{Exploring the relationship between mother household headship and child vaccination rate in Nepal
}
\author{Prabidhik KC\thanks{Harvard University, Cambridge, USA. Email: \href{mailto:prabidhik_kc@college.harvard.edu}{prabidhik_kc@college.harvard.edu}}}

% Date
\date{\today}

\begin{document}

% Title page
\maketitle

% Abstract
\begin{abstract}
I exploit the differences in family member absentees caused by the foreign employement to estimate the effect of mother household headship on child vaccination rate. Using instrumental variable method and data from Nepal Social Inclusion Survey (NSIS) 2018, I find that there is no statistically significant affect on child vaccination rate if the household head is mother instead of father. Even after controlling for education, log wage, ethnicity, I do not find any significant effect in bacterial vaccination and viral vaccination.
\end{abstract}

% Introduction
\section{Introduction}
This section introduces the research question and motivation for the study. It should also provide background information and a brief literature review.

% Data and Methods
\section{Data and Methods}
This section describes the data source(s), variables, and statistical methods used in the analysis. It should also provide information on the study population and sample size.

% Results
\section{Results}
This section presents the results of the analysis, including descriptive statistics and regression output.

% Discussion
\section{Discussion}
This section interprets the results and discusses their implications. It should also highlight the limitations of the study and suggest avenues for future research.

% Conclusion
\section{Conclusion}
This section summarizes the main findings of the study and provides policy recommendations.

% References
\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
